Bee brain size is positively associated with urban lifestyles but not with positive population trends

### 2022-11-22 Manuscript/Ms.Rmd
methods update

@@

## Overview

@@

## Bee species dataset

Our dataset contains measurements of brain weight and body size for bee specimens captured by hand netting in different areas of the East Coast of United States and Europe (i.e., Spain and Netherlands). In total, the dataset includes `r sum(d$individuals)` female individuals from `r nlevels(factor(unique(d$Species)))` species that represent `r nlevels(factor(unique(tax$family)))` different families and `r nlevels(factor(unique(tax$genus)))` genera. We have considered exclusively female specimens as most bees exhibit sexual dimorphism [@shreeves2008] that likely imply intraspecific differences in brain size between male and female individuals.

## Brain and body size measurements

## Species occurrences data

>>>>

This may be also relevant:

Although recent studies challenge the use of absolute brain size as an estimator for behavioral complexity and computational power (Chittka and Niven, 2009, and references therein), many studies have shown correlations between brain size and performance (Deaner et al., 2007; Gronenberg and Couvillon, 2010; Lefebvre and Sol, 2008).

@@

## (a) Overview

@@

## (b) Bee species dataset

Our dataset contains measurements of brain and body size for bee specimens captured by hand netting in different areas of the East Coast of United States and Europe (i.e., Spain and Netherlands). In total, the dataset includes `r sum(d$individuals)` female individuals from `r nlevels(factor(unique(d$Species)))` species that represent `r nlevels(factor(unique(tax$family)))` different families and `r nlevels(factor(unique(tax$genus)))` genera. We only considered female specimens because most bees exhibit sexual dimorphism and behavioral differences between sexes that can be correlated with the size and structure of the brain [@streinzer2013; @roselino2015]. In addition, because brain size can change with age and experience of the different individuals within a species [@durst1994; @withers2008], we limited our sampling to specimens foraging on flowers. Note that 93 of the species used in our study were previously published with their respective trait measurements in @sayol2020.

## (c) Brain and body size measurements

We used as a measurement of brain size the weight of fixed brains. To weight the brains, all collected individuals were kept in cold and sent them to the laboratory where they were identified by expert taxonomists and anesthetise in cold [@crook2013]. Then, heads were removed with a scalpel and placed in a fixative solution (4% paraformaldehyde in 0.1 M phosphate-buffered saline -PBS- pH = 7.4) to avoid degradation. Subsequently, brains were extracted from the head capsule and placed on a petri dish after removing the retina from the optic lobes and cleaning the entire brain of all tracheae and fat bodies. By doing this, we ensured that our brain measurements mainly accounted for neural tissue. We then placed the brains on a small piece of Parafilm® and dried the exceeding fixative solution with Kimwipes® tissues. Finally, within 4 seconds of the liquid removal, we weighted the brains with the help of a microbalance Sartorius Cubis®.

We considered as a proxy of body size the intertegular span (ITS) that represents the distance between the base of the wings (tegulae) on the bee thorax. ITS has been shown to accurately predict body size as it is highly correlated with dry body weight [@cane1987; @kendall2019]. All ITS measurements were conducted with a stereomicroscope (magnification 16 x –80 x ) with a calibrated ocular micrometre (resolution down to 0.02 mm).

## (d) Species occurrences data
